Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-15 paper.qmd
Regenerated S-curve projection with new data

```{r}
#| label: scurve-training
training_data_scurve <- read_rds("data/s_curve/s_curve_training.rds")
```

@@

projected <- as.matrix(training_data_scurve |> select(-ID)) %*% projection

@@

limits <- 1
rng <- range(projected)
projected <- projected/max(abs(rng))
colnames(projected) <- c("P1", "P2")
projected <- data.frame(projected)
obs_labels <- as.character(1:nrow(training_data_scurve))

@@

>>>>

```{r}
#| label: scurve-training
training_data_scurve <- read_rds("data/s_curve/s_curve_training.rds")

training_data_scurve_n <- read_rds("data/s_curve/scurve_simulated_5000.rds")
```

@@

projected <- as.matrix(training_data_scurve_n) %*% projection

@@

limits <- 1
rng <- range(projected)
projected <- projected/max(abs(rng))
colnames(projected) <- c("P1", "P2")
projected <- data.frame(projected)
obs_labels <- as.character(1:nrow(training_data_scurve_n))

@@

axis_labels <- colnames(training_data_scurve_n)
rownames(axes) <- axis_labels
